\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-09 paper/paper.Rnw
editing section 4

If a subject selects multiple plots from the lineup, the p-value has a Bernoulli distribution with a probability $p_{j} = s/m$, where that observer made $s$ selections out of a lineup with $m$ plots \citep{Follett}. In the event that a lineup has observers making different numbers of selections, we have a binomial distribution with different success probabilities, and a Poisson Binomial distribution must be used to calculate the p-value. The probability mass function of a Poisson Binomial distribution can be written as:

\begin{equation} 
\label{pvalue2}
\centering
P(X=x) = \sum_{A \in T_{x}} \prod_{j \in A} p_{j} \prod_{j \in A^{c}} (1-p_{j})
\end{equation}

>>>>

If a subject selects multiple plots from the lineup, the p-value has a Bernoulli distribution with a probability $p_{j} = s/m$, where that observer made $s$ selections out of a lineup with $m$ plots. In the event that a lineup has observers making different numbers of selections, we have a binomial distribution with different success probabilities, and a Poisson Binomial distribution must be used to calculate the p-value demonstrated by \citet{Follett}. The probability mass function of a Poisson Binomial distribution can be written as:

\begin{equation} 
\label{pvalue2}
\centering
P(X \geq x) = 1 - P(X < (x - 1)) = 1 - \sum^{x-1}_{i=0} \left\{\sum_{A \in T_{x}} \prod_{j \in A} p_{j} \prod_{j \in A^{c}} (1-p_{j})\right\}
\end{equation}
